Supplemental Materials, Methods and Results

### 2021-05-06 supp.Rmd
Functions and supplemental tables for Wald tests done

```{r display, results = "hide"}

#########################################################
# Male-male Competition Displays
#########################################################
  # Load data and clean a bit
  Display_1 <- read.table("./data/Display_1.csv", 
                            header=TRUE, sep=",", dec=".", strip.white=TRUE)

@@

   # Fit model
      PredatorAC <- lmer(dL ~ Predator + Population + BodyRegion + Predator:BodyRegion + Predator:Population + (1|ID), data=Predator)
      summary(PredatorAC)
      anova(PredatorAC)

@@

@@

table_style <- function(table){
    table <- table %>% width(j = 1, width = 1) %>% width(j = 2, width = 2.5) %>% 
             align(align = "center", part = "header") %>% 
              align(i = 1:8, j = 1:6, align = "center", part = "body") %>% 
            compose(part = "header", j = 1, value = as_paragraph(as_b("Predator"))) %>% 
             compose( part = "header", j = 2, value = as_paragraph(as_b("Contrast"))) %>% 
            compose(part = "header", j = 3, value = as_paragraph(as_b("F"))) %>%
            compose(part = "header", j = 4, value = as_paragraph(as_b("DF"))) %>% 
            compose(part = "header", j = 5, value = as_paragraph(as_b("p"))) %>% 
            compose(part = "header", j = 6, value = as_paragraph(as_b("p"), as_sub(as_b("Bonferroni")))) %>%
            compose(part = "body", i = 1, j = 2, 
                    value = as_paragraph("Kenya", as_sub("gular"), " - ", "Hawaii", as_sub("gular")))  %>% 
            compose(part = "body", i = 2, j = 2, 
                    value = as_paragraph("Kenya", as_sub("midflank"), " - ", "Hawaii", as_sub("midflank"))) %>% 
            compose(part = "body", i = 3, j = 2, 
                    value = as_paragraph("Kenya", as_sub("tailbase"), " - ", "Hawaii", as_sub("tailbase"))) %>% 
            compose(part = "body", i = 4, j = 2, 
                    value = as_paragraph("Kenya", as_sub("topflank"), " - ", "Hawaii", as_sub("topflank"))) %>% 
            compose(part = "body", i = 5, j = 2, 
                    value = as_paragraph("Kenya", as_sub("gular"), " - ", "Hawaii", as_sub("gular")))  %>% 
            compose(part = "body", i = 6, j = 2, 
                    value = as_paragraph("Kenya", as_sub("midflank"), " - ", "Hawaii", as_sub("midflank"))) %>% 
            compose(part = "body", i = 7, j = 2, 
                    value = as_paragraph("Kenya", as_sub("tailbase"), " - ", "Hawaii", as_sub("tailbase"))) %>% 
            compose(part = "body", i = 8, j = 2, 
                    value = as_paragraph("Kenya", as_sub("topflank"), " - ", "Hawaii", as_sub("topflank")))
 return(table)
}

@@

>>>>

```{r display, results = "hide"}
source("./R/func.R")
#########################################################
# Male-male Competition Displays
#########################################################
  # Load data and clean a bit
  Display_1 <- read.table("./data/Display_1.csv", 
                            header=TRUE, sep=",", dec=".", strip.white=TRUE)

@@

   # Fit model
      PredatorAC <- lmer(dL ~ Predator + Population + BodyRegion + Predator:BodyRegion + Predator:Population + 
                           (1|ID), data=Predator)
      summary(PredatorAC)

  PredatorAC_main <- lmer(dL ~ Predator + Population + BodyRegion  + (1|ID), data=Predator)

  # Wald table RVE

    Wald_table_PredatorAC <- wald_table_p(PredatorAC_main, PredatorAC)

@@

    PredatorCC_main <- lmer(dS ~ Predator + Population + BodyRegion  + (1|ID), data=Predator)

  # Wald table RVE

    Wald_table_PredatorCC <- wald_table_p(PredatorCC_main, PredatorCC)

@@

@@

```{r tableS3, tab.cap = "Wald Tests comparing significance of model parameters. Wald tests computed using robust variance estimators with a Saitterwaite correction to the degrees of freedom. Interactions were first tested and models refit to test the signifiacnce of main effects"}
fullTable <- rbind(wald_table_ConspicDisplayAC, 
                   wald_table_ConspicDisplayCC, 
                   wald_table_ConspicCourtshipAC,
                   wald_table_ConspicCourtshipCC)

fullTable <- fullTable %>% 
              mutate(Context = c("Male-Male Display", rep("", 7), "Courtship Display", rep("", 7)),
                     JND = c("Achromatic Contrast", rep("", 3), "Chromatic Contrast", rep("", 3), "Achromatic Contrast", rep("", 3), "Chromatic Contrast", rep("", 3)),
                     p_val = sapply(p_val, function(x) p_value(x))) %>% select(Context, JND, Variable, Fstat, df_num, df_denom, p_val)

S3 <- flextable(fullTable) %>%
        table_style2(.)
S3
```

```{r table4, tab.cap = "Wald Tests comparing significance of model parameters for predators. Wald tests computed using robust variance estimators with a Saitterwaite correction to the degrees of freedom. Interactions were first tested and models refit to test the signifiacnce of main effects"}

fulltableP <- rbind(Wald_table_PredatorAC,
                    Wald_table_PredatorCC)

fulltableP <- fulltableP %>% mutate(JND = c("Achromatic Contrast", rep("",4), "Chromatc Contrast", rep("",4)),
                                            p_val = sapply(p_val, function(x) p_value(x))) %>% 
                                      select(JND, Variable, Fstat, df_num, df_denom, p_val)

S4 <- flextable(fulltableP) %>%
        table_style3(.)
S4
```
